Staged Abstract Interpreters

### 2018-11-13 paper/30_sai.tex
fix mistake when generating functions

\subsection{Discussion}
what not to do when writing an abstract interpreter for staging?
what kind of abstract interpreter is friendly for staging/specialization?

@@

Big-step vs small-step

@@

>>>>

\subsection{Modular Analysis for Free}

Motivation: one of the challenges of modern static analysis is program usually depends on
large libraries programs\cite{toman_et_al:LIPIcs:2017:7121}. 
Can we analyze programs and libraries separately without losing precision? So that we can 
reduce part of the overhead of repeatedly analyzing libraries for different programs.
Similarly, some static analyzers compute summary for a function or a module, that can be reused
later (like Facebook Infer). But to my knowledge, they are mostly too conservative (context-insensitive) 
or unsound, which both lead to imprecision.

Application: for example, k-CFA (k > 0) is naturally a kind of whole program analysis,
because it is interprocedural and need the last k calling contexts to distinguish
different call sites.
But can we analyze programs (libraries) separately which generate the specialized 
analysis and leave the unavailable programs (for the moment) as dynamic parameters, 
and then install these contexts when we have the whole program.

Another perspective: programs are data for an abstract interpreter, so if we have $n$ programs, 
then maybe there can be $n$ stages. 
Probably we can analyze first $m$ programs, and generate a residual abstract interpreter
waiting for the rest $(n-m)$ programs.
These $(n-m)$ programs might be (abstract) arguments for the first $n$ programs, and
the abstract interpreter itself might be a partial abstract interpreter.

\subsection{Discussion}
Review a little bit what we have done?
what not to do when writing an abstract interpreter for staging?
what kind of abstract interpreter is friendly for staging/specialization?

@@

\paragraph{Big-step vs Small-step.}

@@

\paragraph{Soudness.}
